### 2013-09-29 Rcode/intro.rmd
added first attempt at functions to compute convolution densities and cdfs for unimix to mix.R

Now, we find the fitted values for $\pi$ are mostly near 0, or at 2 (the alternative value).
```{r}
beta.ash$fitted.f
beta.ash.auto$fitted.f
beta.ash.vb.uniform$fitted.f
beta.ash.vb.null$fitted.f
```

@@

Let's try: 
```{r}
beta.ash.pm = ash(ss$betahat, ss$betasd, auto=TRUE, usePointMass=TRUE)
beta.ash.pm$fitted.f
beta.ash.auto$fitted.f
plot(beta.ash.auto$localfsr,beta.ash.pm$localfsr,main="comparison of ash localfsr, with and without point mass",xlab="no point mass", ylab="with point mass",xlim=c(0,1),ylim=c(0,1))
abline(a=0,b=1)
abline(a=0,b=2)
```

>>>>

Now, we find the fitted values for $\pi$ are mostly near 0, or at 2 (the alternative value).
```{r}
print(beta.ash)
print(beta.ash.auto)
print(beta.ash.vb.uniform)
print(beta.ash.vb.null)
```

@@

Let's try: 
```{r}
beta.ash.pm = ash(ss$betahat, ss$betasd, auto=TRUE, usePointMass=TRUE)
print(beta.ash.pm)
print(beta.ash.auto)
plot(beta.ash.auto$localfsr,beta.ash.pm$localfsr,main="comparison of ash localfsr, with and without point mass",xlab="no point mass", ylab="with point mass",xlim=c(0,1),ylim=c(0,1))
abline(a=0,b=1)
abline(a=0,b=2)
```
